\begin{longtable}[htbp]
  \begin{tabularx}{\textwidth}{|l|X|}
    \toprule
    Date & Question \\
    \midrule
    2022/05/26 & ConvertibleTrigger -- what to do if the trigger\_type is unknown \\
    \midrule
    2022/05/27 & StockIssuance -- does cost\_basis make sense here? Is it the per-share basis or total? \\
    \midrule
    2022/05/31 & How does a retraction event work? \\
    \midrule
    2022/06/07 & Various questions about transaction events \\
    \midrule
    2022/06/28 & BaseRepurchase missing balance\_security\_id \\
    \midrule
    2022/06/28 & Clarity around the trigger\_id field on WarrantExercise.schema.json \\
    \midrule
    2022/06/28 & Release transaction enhancements \\
    \midrule
    2022/07/15 & Should TX\_Vesting\_Start Reference the VestingTerms obj id? \\
    \midrule
    2022/07/15 & Should VestingScheduleRelativeTrigger Support Years-Based Vesting Periods? \\
    \midrule
    2022/07/28 & Can some rounding methods create indeterminate vesting for certain VestingTerms? \\
    \midrule
    2022/08/17 & Transitivity of JSON schemas - should BaseSecurityTransaction inherit from BaseTransaction? \\
    \midrule
    2022/08/31 & Create new vesting transaction to represent accelerated vesting \\
    \midrule
    2022/08/31 & Create new vesting transaction to represent stopped / resumed vesting \\
    \midrule
    2022/12/16 & Can you calculate company financial information using OCF? \\
    \midrule
    2023/04/06 & Acceptance Transactions \\
    \midrule
    2023/04/21 & Tracking Discussion for Validation Rules \\
    \midrule
    2023/08/06 & Expected behavior of exercise transaction and transactions in general \\
    \midrule
    2023/08/07 & Transfers when the quantity is spread over multiple security\_ids \\
    \bottomrule
  \end{tabularx}
%  \caption{List of Questions}\label{tab:list-of-questions-ocf-qa}
\end{longtable}